### 2022-01-20 README.Rmd
readme

 - Agreed Data, long form (LINK NEEDED)
 - Agreed Data, wide form (LINK NEEDED)
 - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
    + values may contain multiple entries separating with a semicolon
 - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
    + each row contains identifying information for a coder-crisis-event-sentence
    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
    + each value contains a single entry
 - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.

@@

## Other data inputs:

>>>>

 - Agreed Data, long form (LINK NEEDED)
 - Agreed Data, wide form (LINK NEEDED)
 - [Raw codings](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_coder_crisis_sentence_event_aligned.Rds)
    + the initial codings from different GUI versions adjusted so that sentence numbers are aligned.

@@

## Other data inputs:
 - [Clean data, wide form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_wide_clean.Rds)
    + each row is a coder-crisis-event-sentence (i.e. each time a coder looking at a certain sentence in a certain crisis identified an event) 
    + values may contain multiple entries separating with a semicolon
 - [Clean data, long form](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/data/icb_long_clean.Rds)
    + each row contains identifying information for a coder-crisis-event-sentence
    + the information about that sentence is distributed across multiple rows in the columns _variable_ and _value_
    + each value contains a single entry
